\input style-sheet.tex

\h1{Chapter 1 -- Beast of Burden}



It started when everyone left. I was left at the pool while all my friends didn't get to stay because they all had something to do but that's okay. I was alone in a pool, surrounded by palm trees, clouds and sun with some blue sky. As I sat in that pool with blue and sky all around me, with my black hi top Vans, a black shirt, blue jeans and my jean jacket just a few feet outside the pool. I realized many things even at just 18 would probably never be the same again, but that's okay too.

Lawrence, Z, Jack, with some others were there, they had been with me for almost my entire life now that I care to think about it but man time really does fly. I met them all at 10 or younger, while I am Gold. I was home but I have more than one home you see, I go back and forth from city to suburbs, I was proud of both places I was from. I moved a pretty decent bit I guess as a kid, mainly just while in high school.

Back to myself and others, I had honestly been curious about life, but I didn't realize it wasn't or maybe shouldn’t be a major topic. I was spread too far apart, life also was going too far for me. I had just lost a friend from the city, he was younger than me, I know in books they say death happens, and it does, everyday, and you know things bad have happened to kids which is a terrible thing to hold onto, but you ever think it's gonna be your own friend. He was shot in the back of his head, they got the killers, they were put on trial and the rest is history, but my friend never did come back. So that only taught me to appreciate what I can, when I can a lot more than anything. He wasn’t part of my group, but, I wonder what would have happened if I added him in or at least even tried. It silently, quietly haunted me...I wondered if I could have saved him.

In my main group, Lawrence, a white boy with freckles, hair in his face and being over six feet, he was our big man. Next up, Z him and Lawrence had been friends for as long as I can remember. He was about 6 even, and pretty built, looked like a soccer player, with dark somewhat receded hair. Both were white, tall, Lawrence was a little chubbier then anyone would’ve assumed but by no means was he fat, and he was very smart, always working on a car. Z, was pretty bright himself, played several instruments, had a actually healthy and very, very long relationship and was a pretty solid techman. Jack, a swimmer and pole vault person, was also 6 feet, and was maybe 160 pounds, very lean, maybe too lean, he was a good friend but separate from the main group but he would always be there if needed, no questions asked.

I, unfortunately, stand at only 5’10. Also I am mexican, and Native American and white, so I stood out of the group, I was short, pretty skinny, and brown. I played football, ran track for years too off and on, and not too shabby of a fighter, stood on my own in the group, but as we got older, we all did, but we would always be there if needed. Besides, if I wasn’t in the city, I was only a block or 2 away from each person.

We all were different and nothing would change that, but our differences made us better, like a puzzle, if every piece were the exact same, no picture would truly come out, you need differences. For example, they all smoked, I didn’t. Best part was, they didn’t care, because something so small can't break a brotherhood, and if not a brotherhood, a sort of gang. Even while separated all having completely different lives we all figured it out. Lawrence, that boy could work on cars every day of his life and he would never ever and I mean never get bored of them. Z, that guy could play his instruments and have infinite technology, he wouldn’t complain once. Our friend, Michael, could be left with a basketball court and a ball and nice weather and never care to come back or off the court. I met Mike in middle school, he’s going to the Navy soon, crazy...he used to run a fight club back as a kid. He wasn’t necessarily the toughest but he was pretty smart, his mom and dad were super overprotective but he took advantage of whenever he could get out of the house. Michael and I were the only ethnic people in our group now that I think of it, he was black, with waves and really long and skinny and could ball and catch but he didn’t have the best arm. We never fought against any other kids either. Jack, give that dude a smoke and a track, you’d never see him come off it. Jack and Z were also of mexican descent but, they could pass for whites if they wanted to, they also weren’t mexican in terms of culture or heritage but we didn’t care too much for it, not in the suburbs at least. In Los Angeles, I occasionally had to speak it, I didn’t mind it though, my friends in Los Angeles, The Kids, they all played football, spoke spanish too, but that is a story for another day. Unfortunately I'm not as interesting as them, hand me a book and I’d never care to leave it even if I read it several times.

In all truth, I was alone in many cases and have tons of stories on my own. Some aren’t even mine to tell. I really do enjoy story telling, I guess you could say that's the old soul of me. I personally wish I could know everyone’s story but that would probably be too much to bare. So therefore I dont complain about the ones I do know. Even stories from books and magazines and the ones on the T.V. they’re all just, interesting. From Captain Nemo, all the way to mythology, even to S.E. Hinton’s books.

Anyway, us kids live in separate places, the suburbs remind me more of a smalltown but, they’re called suburbs, I think it's debatable. Back in Los Angeles, it is very different. East Los Angeles is where I lived for two going on three years, and man let me tell you, I wouldn’t trade those years for anything. The heat, the sunsets, the traffic, the smell, everything. It honestly isn’t by any means the best or even close to the best but honestly for that while it was home and I owned it. I made many friends, a few enemies, many crushes, too many. That is one thing about me, I crush and fall for everyone and if not everyone, damn near close. It’s not my fault there are so many pretty girls at my school and around the place.

Besides, all my crushes are pretty, and not just in my own eyes but others. One, is this girl, Nicole. Maybe one of my longest crushes ever in my life, she definitely put a spell on me for far too long, but knowing myself I didn't mind at all. An action I would later deeply regret. She hails from the hometown, also she attended the same school as the rest of the boys, while I was over 40 miles away. I often wondered what it would be like, if I went to school with the suburban kids. They often tell me it wouldn’t go well.

Because...as much as I lived there...in all truth it wasn’t my home anymore. The only real reason I would go back is because of my grandpa, friends and my baby brother, I loved that kid to death and then some more on top of that. I couldn’t wait to watch him grow up.

\bye
\end
